---
output: github_document
---
<!-- # eAtlas &middot; [![Build Status](https://travis-ci.org/layik/eAtlas.svg)](https://travis-ci.org/layik/eAtlas) [![Project Status: WIP](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip) [![PRs Welcome](https://img.shields.io/badge/PRs-welcome-brightgreen.svg)](#) -->


### Development
The front end is an npm package, so if you do not need the backend, having cloned the repo:

```{js}
npm i # or yarn
# and run
npm start
```

The frontend is a [`create-react-app`](https://create-react-app.dev/docs/getting-started/) (CRA) so all the standard commands of CRA appliees.

### R 
The application is a [geopumber](https://github.com/ATFutures/geoplumber) app. That means it is an R powered backend API (think Flask in Python) and a ReactJS front end.

To build the frontend, from an R console:
```{r, eval=FALSE}
library(geoplumber)
gp_build()
```

* if you liket to use Mapbox tiles, you can use a Mapbox API key in `.env.local` file using variable name:
`REACT_APP_MAPBOX_ACCESS_TOKEN = 'API_KEY'`

* in production its better to change the `PRD_URL` in the `Constants.js` file.

Then you can run
```{r, eval=FALSE}
library(geoplumber)
gp_plumb()
```

visit `localhost:8000`

or just run the front using (without any data loaded from local server): `npm i & npm start`

### Docker for production

Repo contains Dockerfile for production. This is again WIP. 

```{sh, eval= FALSE}
# Dockerfile manages your npm/React build steps
# REACT_APP_MAPBOX_ACCESS_TOKEN is required but app should run
docker build -t eatlas .
# then bind plumber's default 8000 port to any of your choice
docker run -d -p 8000:8001 --name eatlas eatlas
````
Use your favourite document server (nginx for example) to proxy requets (more later hopefully).
